%\renewcommand{\theequation}{\theenumi}
%\begin{enumerate}[label=\arabic*.,ref=\theenumi]
The matrix of the veritices of the triangle is defined as
		\begin{align}
			\vec{P} = \myvec{\vec{A} & \vec{B} &\vec{C}}
		\end{align}
		\subsection{Vectors}
\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Obtain the direction matrix of the sides of $\triangle ABC$
	defined as 
		\begin{align}
		\vec{M} = 	\myvec{\vec{A}-\vec{B} & \vec{B}-\vec{C} & \vec{C}-\vec{A}}
		\end{align}
	\\
		\solution 

		\begin{align}
			\vec{M} &= \myvec{\vec{A}-\vec{B} & \vec{B}-\vec{C} & \vec{C}-\vec{A}}
			\\
			&= 
			\myvec{\vec{A} & \vec{B} &\vec{C}}
			\myvec{1 & 0 & -1 \\ -1 & 1 & 0 \\ 0 & -1 & 1}
		\end{align}
		where the second matrix above 
		is known as a {\em circulant} matrix.  Note that the 2nd and 3rd row of the above matrix are circular shifts of the 1st row.
	\item Obtain the normal matrix  of the sides of $\triangle ABC$
		\\
		\solution Considering the roation matrix
		\begin{align}
			\vec{R}  = \myvec{0 & -1 \\ 1 & 0},
		\end{align}
		the normal matrix is obtained as
		\begin{align}
			\vec{N} = \vec{R}\vec{M} 
		\end{align}

	\item Obtain $a, b, c$.
		\\
		\solution The sides vector is obtained as
		\begin{align}
			\vec{d} = \sqrt{\text{diag}(\vec{M}^{\top}\vec{M})}
		\end{align}
	\item Obtain the constant terms in the equations of the sides of the triangle. 
		\\
		\solution The constants for the lines can be expressed in vector form as
		\begin{align}
			\vec{c} = \text{diag}\cbrak{\brak{\vec{N}^{\top}\vec{P}}} 
		\end{align}
\end{enumerate}
		\subsection{Median}
\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Obtain the mid point matrix for the sides of the triangle
	\\
		\solution
		\begin{align}
			\myvec{\vec{D} & \vec{E} &\vec{F}} &= \frac{1}{2}\myvec{\vec{A} & \vec{B} &\vec{C}}
			\myvec{0 & 1 & 1 \\ 1 & 0 & 1 \\ 1 & 1 & 0}
		\end{align}
	\item Obtain the median direction matrix.
\\
\solution The median direction matrix is given by 
		\begin{align}
			\vec{M}_1 &= \myvec{\vec{A}-\vec{D} & \vec{B}-\vec{E} & \vec{C}-\vec{F}}
			\\
			&= 
			  \myvec{
				  \vec{A}-\frac{\vec{B}+\vec{C}}{2} &
			  \vec{B}-\frac{\vec{C}+\vec{A}}{2} &
			  \vec{C}-\frac{\vec{A}+\vec{B}}{2}} 
			  \\
			  &= \myvec{\vec{A} & \vec{B} &\vec{C}}
			  \myvec{
				  1 & -\frac{1}{2} & -\frac{1}{2}
				  \\
				  -\frac{1}{2} & 1 & -\frac{1}{2}
				  \\
				  -\frac{1}{2} & -\frac{1}{2} & 1
				  }
		\end{align}
	\item Obtain the median normal matrix.
	\item Obtian the median equation constants.
	\item Obtain the centroid by finding the intersection of the medians.

\end{enumerate}
		\subsection{Altitude}
\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Find the normal matrix for the altitudes
	\\
		\solution  The desired matrix is 
\begin{align}
	\vec{M}_2 &= 	\myvec{\vec{B}-\vec{C} & \vec{C}-\vec{A} & \vec{A}-\vec{B} }
	\\
	&= 
	\myvec{\vec{A} & \vec{B} &\vec{C}}
			\myvec{ 0 & -1 & 1 \\ 1 & 0 & -1 \\ -1 & 1 & 0}
		\end{align}

	\item Find the constants vector for the altitudes.
		\\
		\solution The desired vector is 
		\begin{align}
			\vec{c}_2 = \text{diag}\cbrak{\brak{\vec{M}^{\top}\vec{P}}} 
		\end{align}
\end{enumerate}
		\subsection{Perpendicular Bisector}
\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Find the normal matrix for the perpendicular bisectors
	\\
	\solution The normal matrix is $\vec{M}_2$
\item Find the constants vector for the perpendicular bisectors.
		\\
		\solution The desired vector is 
		\begin{align}
			\vec{c}_3 = \text{diag}\cbrak{\vec{M}_2^{\top}\myvec{\vec{D} & \vec{E} &\vec{F}}}
		\end{align}

\end{enumerate}
		\subsection{Angle Bisector}
\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
\numberwithin{equation}{enumi}
\item Find the points of contact.
	\\
		\solution The points of contact are given by 
		\begin{align}
			\myvec{			\frac{n\vec{A}+p\vec{C}}{n+p}
			&
						\frac{p\vec{B}+m\vec{A}}{p+m}
						&
						\frac{m\vec{C}+n\vec{B}}{m+n}
			}
			= 	\myvec{\vec{A} & \vec{B} &\vec{C}}
			\myvec{
				\frac{n}{b} & \frac{m}{c} & 0
				\\
0 & \frac{p}{c} & \frac{n}{a} 
				\\
				\frac{p}{b} & 0 & \frac{m}{a}
			}
		\end{align}
\end{enumerate}
